Do NBA Teams Avoid Trading within Their Own Division?^[We appreciate feedback we received on this paper from Skye Bender-deMoll, Pavel Krivitsky and David Schaefer.]

### 2022-01-06 Manuscript.Rmd
Generate table in the appendix

---
title: "Do NBA Teams Avoid Trading within Their Own Division?^[We appreciate feedback we received on this paper from Skye Bender-deMoll, Pavel Krivitsky and David Schaefer.]"
author: 
  - first_name: Jimi
    last_name: Adams
    orcid_id: "0000-0001-5043-1149"
    affiliation: University of Colorado
  - first_name: Michał
    last_name: Bojanowski
    orcid_id: "0000-0001-7503-852X"
    affiliation: Kozminski University
date: November 29, 2021
description: "Within US professional sports, trades within one's own division are often perceived to be disadvantageous. We ask how common this practice is. To examine this question, we construct a date-stamped network of all trades in the NBA between June 1976 and May 2019. We then use yearly weighted exponential random graph models to estimate the likelihood of teams avoiding within-division trade partners, and whether that pattern changes through time. In addition to the empirical question, this analysis serves to demonstrate the necessity and difficulty of constructing the proper baseline for statistical comparison. We find limited-to-no support for the popular perception."
output: 
  distill::distill_article:
    code_folding: true
link-citations: true
bibliography: nba_trades.bib
---

@@

Table: Full results for the ERG model fit to pooled data.

|Effect                |   Estimate|        SE|95% CI         | p-value|
|:---------------------|----------:|---------:|:--------------|-------:|
|*Seasonal base rates* |           |          |               |        |
|1976-1977             | -0.9026534| 0.0792530|(-1.06; -0.75) |   0.000|
|1977-1978             | -0.8427925| 0.0724760|(-0.98; -0.70) |   0.000|
|1978-1979             | -0.9263500| 0.0796106|(-1.08; -0.77) |   0.000|
|1979-1980             | -0.8762352| 0.0771426|(-1.03; -0.73) |   0.000|
|1980-1981             | -0.9910653| 0.0854415|(-1.16; -0.82) |   0.000|
|1981-1982             | -0.9050884| 0.0754043|(-1.05; -0.76) |   0.000|
|1982-1983             | -0.8069531| 0.0682278|(-0.94; -0.67) |   0.000|
|1983-1984             | -0.9092292| 0.0766022|(-1.06; -0.76) |   0.000|
|1984-1985             | -1.0526877| 0.0872369|(-1.22; -0.88) |   0.000|
|1985-1986             | -1.0782139| 0.0930195|(-1.26; -0.90) |   0.000|
|1986-1987             | -0.9198185| 0.0757693|(-1.07; -0.77) |   0.000|
|1987-1988             | -0.9403157| 0.0781448|(-1.09; -0.79) |   0.000|
|1988-1989             | -1.1192392| 0.0854069|(-1.29; -0.95) |   0.000|
|1989-1990             | -1.1674130| 0.0852806|(-1.33; -1.00) |   0.000|
|1990-1991             | -1.1015000| 0.0789942|(-1.26; -0.95) |   0.000|
|1991-1992             | -1.3314738| 0.1014767|(-1.53; -1.13) |   0.000|
|1992-1993             | -1.2131200| 0.0885597|(-1.39; -1.04) |   0.000|
|1993-1994             | -1.2949074| 0.0953019|(-1.48; -1.11) |   0.000|
|1994-1995             | -1.3952511| 0.1080338|(-1.61; -1.18) |   0.000|
|1995-1996             | -1.2254082| 0.0852894|(-1.39; -1.06) |   0.000|
|1996-1997             | -1.2243585| 0.0837553|(-1.39; -1.06) |   0.000|
|1997-1998             | -1.1148373| 0.0727527|(-1.26; -0.97) |   0.000|
|1998-1999             | -1.2492779| 0.0861211|(-1.42; -1.08) |   0.000|
|1999-2000             | -1.2789135| 0.0904522|(-1.46; -1.10) |   0.000|
|2000-2001             | -1.0430409| 0.0700097|(-1.18; -0.91) |   0.000|
|2001-2002             | -1.0608807| 0.0696335|(-1.20; -0.92) |   0.000|
|2002-2003             | -1.2653868| 0.0888219|(-1.44; -1.09) |   0.000|
|2003-2004             | -1.0915922| 0.0733866|(-1.24; -0.95) |   0.000|
|2004-2005             | -1.0507651| 0.0685301|(-1.19; -0.92) |   0.000|
|2005-2006             | -1.0769347| 0.0703190|(-1.21; -0.94) |   0.000|
|2006-2007             | -1.1925306| 0.0774736|(-1.34; -1.04) |   0.000|
|2007-2008             | -1.1603188| 0.0759557|(-1.31; -1.01) |   0.000|
|2008-2009             | -0.9697841| 0.0623303|(-1.09; -0.85) |   0.000|
|2009-2010             | -0.9605862| 0.0613118|(-1.08; -0.84) |   0.000|
|2010-2011             | -0.9335487| 0.0588953|(-1.05; -0.82) |   0.000|
|2011-2012             | -1.1465080| 0.0721213|(-1.29; -1.01) |   0.000|
|2012-2013             | -0.9791587| 0.0622563|(-1.10; -0.86) |   0.000|
|2013-2014             | -0.9789426| 0.0643977|(-1.11; -0.85) |   0.000|
|2014-2015             | -0.8316791| 0.0542273|(-0.94; -0.73) |   0.000|
|2015-2016             | -1.0257114| 0.0647017|(-1.15; -0.90) |   0.000|
|2016-2017             | -1.0875715| 0.0680398|(-1.22; -0.95) |   0.000|
|2017-2018             | -1.0105469| 0.0640282|(-1.14; -0.89) |   0.000|
|2018-2019             | -0.9172200| 0.0586872|(-1.03; -0.80) |   0.000|
|*Homophily*           |  0.0099434| 0.0587577|(-0.11;  0.13) |   0.866|

>>>>

---
title: "Do NBA Teams Avoid Trading within Their Own Division?^[We appreciate feedback we received on this paper from Skye Bender-deMoll, Pavel Krivitsky and David Schaefer.]"
author: 
  - first_name: Jimi
    last_name: Adams
    orcid_id: "0000-0001-5043-1149"
    affiliation: University of Colorado
  - first_name: Michał
    last_name: Bojanowski
    orcid_id: "0000-0001-7503-852X"
    affiliation: Kozminski University
date: November 29, 2021
description: "Within US professional sports, trades within one's own division are often perceived to be disadvantageous. We ask how common this practice is. To examine this question, we construct a date-stamped network of all trades in the NBA between June 1976 and May 2019. We then use yearly weighted exponential random graph models to estimate the likelihood of teams avoiding within-division trade partners, and whether that pattern changes through time. In addition to the empirical question, this analysis serves to demonstrate the necessity and difficulty of constructing the proper baseline for statistical comparison. We find limited-to-no support for the popular perception."
output: 
  distill::distill_article:
    code_folding: false
link-citations: true
bibliography: nba_trades.bib
---

@@

```{r}
withr::with_options(
  list(knitr.kable.NA = ""), {
    knitr::kable(
      readRDS(file = "model1-table.rds"), 
      caption = "Full results for the ERG model fit to pooled data.",
      align = "lrrrr")
  })
```
